Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-01-11 paperIEEE.tex
Canvas/layout example figure and text
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@75 db7c848b-7755-4df2-b763-8796797afa52

\FIXME{Highlight integration of many features into a general framework vs
one-off research implementation of one algorithm. Also point out the various and
very diverse examples in Section 7, highlighting the variety of application and
implementation scenarios that can benefit from \textsf{Equalizer}.}

@@

We do present novel algorithms for parallel rendering which did not warrant a
separate publication: pixel and subpixel decompositions, dynamic frame
resolution, tunable sort-first load-balancing parameters, frame rate
equalization, thread synchronization modes for multi-threaded rendering, dynamic
focus distance and asymmetric eye positions for Virtual Reality, parallel pixel
streaming to tiled display walls, as well as a fully-fledged data distribution
API with compression and reliable multicast.

@@

% A view may have a frustum description. The view's frustum overrides frusta
% specified at the canvas or segment level. This is used for non-physically
% correct rendering, e.g., to compare two models side-by-side on a tiled display
% wall. If the view does not specify a frustum, the corresponding destination
% channels will use the physically correct sub-frustum resulting from the
% view/segment intersection.

@@

@@

\textsf{Collage} provides networking functionality of different abstraction
layers,
gradually providing higher level functionality for the programmer. The main
primitives in \textsf{Collage} are:

@@

\begin{figure}[ht]\center
  \includegraphics[width=\columnwidth]{images/netObject}
  \caption{\label{fNetObject}Communication between two \textsf{Collage} objects}
\end{figure}
\fig{fNetObject} illustrates this architecture.

>>>>

@@

We do present novel algorithms for parallel rendering which did not warrant a
separate publication: pixel and subpixel decompositions, dynamic frame
resolution, tunable sort-first load-balancing parameters, frame rate
equalization, thread synchronization modes for multi-threaded rendering, a
powerful abstraction for multi-view rendering on arbitrary display setups,
dynamic focus distance and asymmetric eye positions for Virtual Reality,
parallel pixel streaming to tiled display walls, as well as a fully-fledged data
distribution API with compression and reliable multicast.

@@

@@

\begin{figure}[ht]\center
  \includegraphics[width=\columnwidth]{images/layout}
  \caption{\label{fLayout}A 2x2 tiled display wall and control host rendering four independent views driven by an eight node visualization cluster}
\end{figure}

\fig{fLayout} shows RTT Deltagen running an example multi-segment, multi-view
setup driven by eight rendering nodes. The main tiled display wall canvas uses
four LCD segments showing one layout with four views, which do not align on the
segment boundaries. This setup creates seven destination channels. The
configuration provides multiple, run-time configurable layouts. It is driven
from the control host on the right, which shows four views, each in their own
canvas and segment windows with a single-view layout each. One view on the
control host synchronizes its content (model and camera) with one view on the
display wall through Collage objects. The control host allows full model
modifications and all workflows supported within the standalone Deltagen
application, and all changes are synchronized to the corresponding rendering
nodes. Since this setup is monoscopic, no head tracking or observers are used.

@@

\textsf{Collage} provides networking functionality of different abstraction
layers, gradually providing higher level functionality for the programmer. The
main primitives in \textsf{Collage} and their relation are shown in
\fig{fNetObject} and provide:

@@

\begin{figure}[ht]\center
  \includegraphics[width=\columnwidth]{images/netObject}
  \caption{\label{fNetObject}Communication between two \textsf{Collage} objects}
\end{figure}
